\section{Functions}

    I assume you already know about functions; this is what their basic syntax looks like in Python:

    \mypy{content/partials/functions/basic_syntax.py}
    \mytext{content/partials/functions/basic_syntax.out}

    You can also set default parameters by saying
    \mintinline{python}{def my_function(x=1, y=1):}
    so you can call the function with zero, one or two arguments.
    Parameters with a default value are \textbf{optional arguments}, those without are called
    \textbf{positional arguments}.

    Note that \textbf{optional parameters} must be the last arguments in the function definition.
    So \mintinline{python}{def my_function(x=1, y):} is not a valid definition.

    Furthermore, you can \textbf{specify the desired data types} of the function arguments with
    \mintinline{python}{def my_function(x: int, y: int) -> int:}.
    However, everyone's still able to pass variables of any kind to that function,
    meaning \textbf{the data type is not enforced} by any means but just
    for documentation and readability!

    \mypy{content/partials/functions/parameters.py}
    \mytext{content/partials/functions/parameters.out}

    If you wanted to return two items you'd usually return a tuple instead of a list like I did,
    so we'll revisit this function later and improve it when we talk about tuple unpacking.

    As you can see on line 9 you can \textbf{set a parameter by its variable name}
    instead of position.
    This is especially useful when working with functions which can have a huge number of optional
    arguments and you need to only set some specific ones.

    \subsection{Arbitrary Argument Lists}

        Sometimes you want to be able to call a function with any number of variables;
        in Python, this is done with *args and you might know this concept from other programming
        languages as 'varargs' (variables arguments).

        Let's take a function \mintinline{python}{my_sum()} as an example:

        \mypy{content/partials/functions/my_sum.py}
        \mytext{content/partials/functions/my_sum.out}

        The function \mintinline{python}{my_sum()} stores all the values it gets in the *args list.
        The * denotes that the variables called 'args' takes all the spare values; The * variables must
        be written after all the positional and optional arguments.
        it is later accessed by just using \mintinline{python}{args}, not \mintinline{python}{*args}!

    \subsection{Keyword Arguments}
        Arbitrary argument lists contain a list of spare values, keyword arguments, on the other hand,
        are dictionaries containing spare values set in the function call with the
        \mintinline{python}{key=value} syntax.

        \mypy{content/partials/functions/kwargs.py}
        \mytext{content/partials/functions/kwargs.out}

        Note that \textit{item} is not a keyword argument, as \textit{item} is a normal variable
        from the function definition, however, its value can still be set using the
        \mintinline{python}{key=value} syntax in the function call.



    \subsection{Lambdas}
        Lambdas are a shorthand for one-line functions and created using the
        \mintinline{python}{lambda} keyword. They receive variables and their function body consists
        of only one term, which value also gets returned, therefore an explicit
        \mintinline{python}{return} is not needed.

        For typical use cases, see \fullref{Common Built-In Functions}

        \mypy{content/partials/functions/lambda.py}
        \mytext{content/partials/functions/lambda.out}
